### 2023-06-09 resilience.tex
up

\alain{faire le lien avec home space, et les formules dans Schnoebelen}

% Linked problems
{\bf Related problems.} 
A set of configurations $H$ is an {\em home-space} for a set of configurations $X$ if every configuration reachable from $X$ can reach $H$. Resilience as introduced above essentially asks whether $\Safe$ is a home-space for $\Bad$, whereas $k$-resilience and bounded-resilience focus more on the length of the paths from $\Bad$ to $\Safe$. The home-space problem is decidable for
Petri nets when $X$ and $H$ are both semilinear sets~\cite{DBLP:journals/corr/abs-2207-02697}.
To these author's knowledge, there are no general results for home-space in WSTS.

@@

% The Model-checking problem for LTL, CTL*, etc. is a natural generalization of the reachability problem. This problem is undecidable in general but there are simple formulae decidable

@@

\begin{remark}[Reformulation]\label{reformulation}
$\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
(\Safe, \Bad)-resilient iff $\Bad \subseteq \pred^*(\Safe)$.\\
$\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
(\Safe, \Bad)-$k$-resilient iff $\Bad \subseteq \pred^{\leq k}(\Safe)$.
\end{remark}

>>>>

{\bf Related problems.} 
A set of configurations $H$ is an {\em home-space} for a set of configurations $X$ if every configuration reachable from $X$ can reach $H$. Resilience as introduced above essentially asks whether $\Safe$ is a home-space for $\Bad$, whereas $k$-resilience and bounded-resilience focus more on the length of the paths from $\Bad$ to $\Safe$. The home-space problem is decidable for
Petri nets when $X$ and $H$ are both semilinear sets~\cite{DBLP:journals/corr/abs-2207-02697}.
To these author's knowledge, there are no general results for home-space in WSTS.

@@

@@

% \begin{remark}[Reformulation]\label{reformulation}
% $\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
% (\Safe, \Bad)-resilient iff $\Bad \subseteq \pred^*(\Safe)$.\\
% $\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
% (\Safe, \Bad)-$k$-resilient iff $\Bad \subseteq \pred^{\leq k}(\Safe)$.
% \end{remark}
